A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-10 05_severity_metaAnalysis.Rmd
add boxplot
Update MA to use disease severity data set including all trials with V

# Data
load("cache/PrepData.Rdata")
```

Which trials don't have all the required variance information?
```{r noDiseaseError}
unique(PM_MB_dat_full[is.na(PM_MB_dat_full$disease_error),
                      c("trial_ref", "location", "year")])
```

Eliminate trials with out disease severity variance.
```{r rm_SevDiseaseError}
PM_sev <- 
   PM_MB_dat_full %>%
   filter(is.na(disease_error) == FALSE)
```
Are all the reported disease variance the same type?
```{r sev_var_type}
unique(PM_sev[,"D_error_type"])
```

@@

>>>>

# Data
PM_dat_D <-
   read.csv("cache/PM_disease_clean_data.csv", stringsAsFactors = FALSE)
```

Which trials don't have all the required variance information?
```{r noDiseaseError}
unique(PM_dat_D[is.na(PM_dat_D$d_vi),
                      c("trial_ref", "location", "year")])
```

Eliminate trials with out disease severity variance.
```{r rm_SevDiseaseError}
PM_sev <- 
   PM_dat_D %>%
   filter(is.na(d_vi) == FALSE)
```
Are all the reported disease variance the same type?
```{r sev_var_type}
unique(PM_sev[,"D_error_type"])
```

@@

Inspect raw disease severity scores

```{r PMsev_bwplot}
PM_sev %>%
   ggplot(aes(x = spray_management, y = PM_final_severity)) +
   geom_boxplot()
```
